---
title: "Descriptive Tables"
output:
  html_notebook:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: simplex
    number_sections: true
    highlight: zenburn
    fig_width: 8
    fig_height: 6
    css: custom.css
  html_document:
    toc: true
    toc_depth: '4'
    df_print: paged
---

```{r warning=FALSE, message=FALSE}
rm(list = ls())
library(tidyverse)
library(tableone)
library(openxlsx)
library(sjPlot)
library(knitr)
library(magrittr)
library(gtsummary)
library(janitor)
```

# Data Setup 
```{r}
# Load data from pre-processed clean rds files
# file path -> "data/rds/xxx"
demo <- readRDS("data/rds/demo.rds")
locations = readRDS("data/rds/locations.rds")
group <- readRDS("data/rds/group.rds")
itt <- readRDS("data/rds/itt_full.rds")
surv <- readRDS("data/rds/surv1.rds") # load survival related data

# Create main data file for tables
demo = left_join(demo, group, by = "sid") # add group variable
demo = left_join(demo, surv, by = "sid") # add surv variables
demo = left_join(demo, locations, by = "sid") # add location variables
```

```{r}
# Sanity check: print out the data statistics
tabyl(group$group) # table out group assignment
tabyl(itt$randomized) # table out randomized
tabyl(itt$received_study_drug_any_amount_y_n) # table out received study drug
tabyl(itt$analysis_population_m_itt) # table out mITT population
tabyl(itt$analysis_population_pp) # table out PP population
tabyl(itt$analysis_population_safety) # table out safety population
```
# mITT analytical set
```{r}
# analytical sets
mitt = itt %>% filter(analysis_population_m_itt == 'Y') # ITT
itt_standard = itt %>% filter(randomized == 'Y' & received_study_drug_any_amount_y_n == 'Y') # mITT
pp = itt %>% filter(analysis_population_pp == 'Y') # per protocol

# save
saveRDS(mitt, "data/rds/mitt.rds")
saveRDS(itt_standard, "data/rds/itt.rds")
saveRDS(pp, "data/rds/pp.rds")
```

# Use mITT set
```{r}
# define sample
sample = mitt
# we can assign other options if we want to double check:
  # sample = itt
  # sample = pp

# Create table using tableone
demo = demo %>% filter(sid %in% sample$sid)

# for all variable like "med_prestudy_" or "med_duringstudy_":
# we will create a new binary variable that indicate if value>0, and create new variables with "_yn", but value as 0/1

new_yn_vars = c(
  "med_prestudy_opioids_yn",
  "med_prestudy_benzos_yn",
  "med_prestudy_phenobarbital_yn",
  "med_prestudy_chlordiazepoxide_yn",
  "med_prestudy_antipsychotics_yn",
  "med_prestudy_propofol_yn",
  "med_prestudy_ketamine_yn",
  "med_prestudy_dexmedetomidine_yn",
  "med_prestudy_melatonin_yn",
  
  "med_duringstudy_opioids_yn",
  "med_duringstudy_benzos_yn",
  "med_duringstudy_phenobarbital_yn",
  "med_duringstudy_chlordiazepoxide_yn",
  "med_duringstudy_antipsychotics_yn",
  "med_duringstudy_propofol_yn",
  "med_duringstudy_ketamine_yn",
  "med_duringstudy_dexmedetomidine_yn",
  "med_duringstudy_melatonin_yn"
)
```

# Set up table data 
```{r}
# Set up Table 1 as tdata
tdata = demo

# combine Dex group together -> 2 groups
tdata$group2g = case_when(
  tdata$group == "Dex 0.1 mcg/kg/h" ~ "Dex",
  tdata$group == "Dex 0.3 mcg/kg/h" ~ "Dex",
  TRUE ~ tdata$group
)
# placebo as ref
tdata$group2g <- relevel(factor(tdata$group2g), ref = "Placebo")

# def 3groups
tdata = tdata %>% rename(group3g = group)
tdata$group3g <- relevel(factor(tdata$group3g), ref = "Placebo")
```

# select 2g or 3g groups
```{r}
# then correctly mark 2 groups vs 3 groups
tdata = tdata %>% mutate(groupx = group2g) # --> 2 groups
# tdata = tdata %>% mutate(groupx = group3g) # --> 3 groups
```

```{r}
# additional clean up

# re-level them use "N" as the reference group
tdata$cardiac_dysfunction = relevel(factor(tdata$cardiac_dysfunction), ref = "N")
tdata$delirium_status = relevel(factor(tdata$delirium_status), ref = "N")
tdata$obstructive_sleep_apnea_y_n = relevel(factor(tdata$obstructive_sleep_apnea_y_n), ref = "N")
tdata$history_of_depression_y_n = relevel(factor(tdata$history_of_depression_y_n), ref = "N")
tdata$any_location_surgical = relevel(factor(tdata$any_location_surgical), ref = "N")

# also recode all med ... yn variables to factor and use N as the reference group, use case_when
tdata <- tdata %>%
  mutate(across(
    .cols = new_yn_vars,
    .fns = ~ factor(
      case_when(
        . == 0 ~ "N",
        . == 1 ~ "Y",
        TRUE    ~ NA_character_  # in case of missing or unexpected values
      ),
      levels = c("N", "Y")
    )
  ))
```

```{r}
# set up variables
baseline_vars = c(
  "age",
  "sex",
  "race",
  "ethnicity",
  "education",
  "mean_iqcode_score",
  "cci_cci_score_weighted",
  "lawton_iadl_total_score_0_8",
  "primary_diagnosis",
  "weight",
  "day_1_sofa_score",
  "cardiac_dysfunction",
  "nrs_sleep_score",
  "delirium_status",
  "obstructive_sleep_apnea_y_n",
  "history_of_depression_y_n",
  "extubation_status",
  "any_location_surgical",
  "days_in_icu_pre_enrollment",
  "days_in_hosp_pre_enrollment",
  
  "med_prestudy_opioids_yn",
  "med_prestudy_benzos_yn",
  "med_prestudy_phenobarbital_yn",
  "med_prestudy_chlordiazepoxide_yn",
  "med_prestudy_antipsychotics_yn",
  "med_prestudy_propofol_yn",
  "med_prestudy_ketamine_yn",
  "med_prestudy_dexmedetomidine_yn",
  "med_prestudy_melatonin_yn"
)

during_vars = c(
  "icu_los_for_icu_admission_during_which_the_pt_was_enrolled",
  "hosp_los",
  "deposition_outcome",
  "mortality_in_icu",
  "survival_days_in_icu",
  "mortality_in_hosp",
  "survival_days_in_hosp",
  "days_from_date_time_enrolled_to_date_time_death",
  "days_from_date_time_first_study_drug_administration_to_date_time_death",
  "mortality_within_14d_from_date_enrolled",
  "mortality_within_14d_from_first_med_adm",
  "mortality_within_12_months_from_date_enrolled",
  "readmit_30d_discharge",
  "med_duringstudy_opioids_yn",
  "med_duringstudy_benzos_yn",
  "med_duringstudy_phenobarbital_yn",
  "med_duringstudy_chlordiazepoxide_yn",
  "med_duringstudy_antipsychotics_yn",
  "med_duringstudy_propofol_yn",
  "med_duringstudy_ketamine_yn",
  "med_duringstudy_dexmedetomidine_yn",
  "med_duringstudy_melatonin_yn",
  "adj_icu_coma_days",
  "adj_in_hosp_coma_days"
)

# names(demo) %>% dput() # output for check
```

```{r}
# add labels
library(labelled)
tdata <- tdata %>% set_variable_labels(
         age = "Age, years",
         sex = "Sex, female",
         race = " Race",
         ethnicity = "Ethnicity",
         education = "Education, years",
         mean_iqcode_score = "IQCODE-SF score (1-5)",
         cci_cci_score_weighted = "CCI score (weighted)",
         lawton_iadl_total_score_0_8 = "Lawton iADL total score (0-8)",
         primary_diagnosis = "Primary diagnosis for ICU admission",
         weight = "Weight, kg",
         day_1_sofa_score = "SOFA score (0-24) at enrollment",
         cardiac_dysfunction = "Presence of any significant reported cardiac dysfunction",
         nrs_sleep_score = " NRS-Sleep score (0-10) for sleep quality",
         obstructive_sleep_apnea_y_n = "Obstructive sleep apnea (OSA) diagnosis",
         history_of_depression_y_n = "History of depression",
         extubation_status = "Non-intubated at enrollment",
         delirium_status = "Delirious or coma on day of enrollment",
         any_location_surgical = "Admitted to a surgical ICU at enrollment",
         days_in_icu_pre_enrollment = "Days in ICU pre-enrollment",
         days_in_hosp_pre_enrollment = "Days in hospital pre-enrollment",
         
         med_prestudy_opioids_yn = "Prestudy Opioids",
         med_prestudy_benzos_yn = "Prestudy Benzodiazepines",
         med_prestudy_phenobarbital_yn = "Prestudy Phenobarbital",
         med_prestudy_chlordiazepoxide_yn = "Prestudy Chlordiazepoxide",
         med_prestudy_antipsychotics_yn = "Prestudy Antipsychotics",
         med_prestudy_propofol_yn = "Prestudy Propofol",
         med_prestudy_ketamine_yn = "Prestudy Ketamine",
         med_prestudy_dexmedetomidine_yn = "Prestudy Dexmedetomidine",
         med_prestudy_melatonin_yn = "Prestudy Melatonin",
         
         mortality_within_14d_from_date_enrolled = "Mortality within 14 days from date enrolled",
         mortality_within_14d_from_first_med_adm = "Mortality within 14 days from first study drug adm",
         days_from_date_time_enrolled_to_date_time_death = "Days from enrollment to death",
         days_from_date_time_first_study_drug_administration_to_date_time_death = "Days from first study drug admin to death",
         mortality_in_icu = "Mortality in ICU",
         mortality_in_hosp = "Mortality in Hospital",
         mortality_within_12_months_from_date_enrolled = "Mortality within 12 months from date enrolled",
         readmit_30d_discharge = "Readmission within 30 days from discharge",
         adj_in_hosp_coma_days = "Adjusted In-hospital Coma Days",
         adj_icu_coma_days = "Adjusted ICU Coma Days",
         icu_los_for_icu_admission_during_which_the_pt_was_enrolled = "ICU LOS",
         hosp_los = "In-Hospital LOS",
         deposition_outcome = "Deposition Outcome",
         
         survival_days_in_icu = "If died, Survival Days in ICU",
         survival_days_in_hosp = "If died, Survival Days in Hospital",
         
         med_duringstudy_opioids_yn = "During-study Opioids",
         med_duringstudy_benzos_yn = "During-study Benzodiazepines",
         med_duringstudy_phenobarbital_yn = "During-study Phenobarbital",
         med_duringstudy_chlordiazepoxide_yn = "During-study Chlordiazepoxide",
         med_duringstudy_antipsychotics_yn = "During-study Antipsychotics",
         med_duringstudy_propofol_yn = "During-study Propofol",
         med_duringstudy_ketamine_yn = "During-study Ketamine",
         med_duringstudy_dexmedetomidine_yn = "During-study Dexmedetomidine",
         med_duringstudy_melatonin_yn = "During-study Melatonin"
)
```

```{r}
# set variables
norm_var = c(
  "mean_iqcode_score",
  "cci_cci_score_weighted"
)

nonnorm_var = c(
  "age",
  "education",
  "lawton_iadl_total_score_0_8",
  "weight",
  "day_1_sofa_score",
  "cardiac_dysfunction",
  "adj_in_hosp_coma_days",
  "adj_icu_coma_days",
  "nrs_sleep_score",
  "weight",
  "days_in_icu_pre_enrollment",
  "days_in_hosp_pre_enrollment",
  "icu_los_for_icu_admission_during_which_the_pt_was_enrolled",
  "hosp_los",
  "survival_days_in_icu",
  "survival_days_in_hosp",
  "days_from_date_time_enrolled_to_date_time_death",
  "days_from_date_time_first_study_drug_administration_to_date_time_death"
)

cat_var = c(
  "sex",
  "race",
  "ethnicity",
  "primary_diagnosis",
  "cardiac_dysfunction",
  "delirium_status",
  "obstructive_sleep_apnea_y_n",
  "history_of_depression_y_n",
  "extubation_status",
  "any_location_surgical",
  "deposition_outcome",
  "mortality_within_14d_from_date_enrolled",
  "mortality_within_12_months_from_date_enrolled",
  "readmit_30d_discharge",
  "mortality_in_icu",
  "mortality_in_hosp",
  "adj_in_hosp_coma_days", # very few levels
  "adj_icu_coma_days" # very few levels
)

cat_var = c(cat_var,new_yn_vars)
```

# Table 1 & 2
```{r}
# Create table using tableone

table1 = CreateTableOne(vars = baseline_vars, data = tdata, factorVars = cat_var, strata = "groupx")
table1p = print(table1, nonnormal = nonnorm_var, normal = norm_var, smd = T, , test = F, catDigits = 1, contDigits = 1,showAllLevels = F,
                varLabels = T)
table1p = print(table1, nonnormal = nonnorm_var, normal = norm_var, smd = F, , test = T, catDigits = 1, contDigits = 1,showAllLevels = F,
                varLabels = T)

# cleanup table1 and table1p from memory to avoid confusion
rm(table1, table1p)
```
# table 3
```{r}
table1 = CreateTableOne(vars = during_vars, data = tdata, factorVars = cat_var, strata = "groupx", test = F)
table1p = print(table1, nonnormal = nonnorm_var, normal = norm_var, smd = F, catDigits = 1, contDigits = 1,showAllLevels = F,
                varLabels = T)
# cleanup table1 and table1p from memory to avoid confusion
rm(table1, table1p)
```

# table 3 regressions
```{r}
# during_vars %>% dput()

yn_vars = c("mortality_in_icu", "mortality_within_14d_from_date_enrolled", "mortality_within_14d_from_first_med_adm",
"mortality_in_hosp", "mortality_within_12_months_from_date_enrolled", "readmit_30d_discharge",
"med_duringstudy_opioids_yn", "med_duringstudy_benzos_yn", 
"med_duringstudy_phenobarbital_yn", "med_duringstudy_chlordiazepoxide_yn", 
"med_duringstudy_antipsychotics_yn", "med_duringstudy_propofol_yn", 
"med_duringstudy_ketamine_yn", "med_duringstudy_dexmedetomidine_yn", 
"med_duringstudy_melatonin_yn")

num_vars = c("survival_days_in_icu", "survival_days_in_hosp", "adj_in_hosp_coma_days", "adj_icu_coma_days")
```

```{r}
library(gtsummary)
library(gt)

# set up regression data --> tdata2
tdata2 = tdata
# function to recode Y/N to 1/0
recode_yn_to_binary <- function(x) {
  case_when(
    x == "Y" ~ 1,
    x == "N" ~ 0,
    TRUE      ~ NA_real_  # in case of missing or unexpected values
  )
}

# do that to all during_vars that are in cat_var
for (var in during_vars) {
  if (var %in% yn_vars) {
    tdata2[[var]] <- recode_yn_to_binary(tdata2[[var]])
  }
}

# deceased as ref
tdata2$deposition_outcome <- relevel(factor(tdata2$deposition_outcome), ref = "Deceased")

# factor adj_in_hosp_coma_days as 0->14 levels
tdata2$adj_in_hosp_coma_days_cat <- factor(tdata2$adj_in_hosp_coma_days,ordered = T, levels = c(0,1,2,4,8))
tdata2$adj_icu_coma_days_cat <- factor(tdata2$adj_icu_coma_days,ordered = T, levels = c(0,1,2,3))
```

##  Length of stay in ICU
```{r}
mod_nb_icu <- MASS::glm.nb(
  icu_los_for_icu_admission_during_which_the_pt_was_enrolled ~ groupx,
  data = tdata2
)

tbl_regression(
  mod_nb_icu,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>% 
  modify_header(estimate = "**IRR (95% CI)**") %>%
  as_gt() %>%
  gt::tab_header(title = "ICU LOS")
```

## In-hospital LOS
```{r}
mod_nb_hosp <- MASS::glm.nb(
  hosp_los ~ groupx,
  data = tdata2
)

tbl_regression(
  mod_nb_hosp,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>% 
  modify_header(estimate = "**IRR (95% CI)**") %>%
  as_gt() %>%
  gt::tab_header(title = "Hospital LOS")
```

##  Disposition outcome
```{r}
library(nnet)
mod_multi <- multinom(deposition_outcome ~ groupx, data = tdata2)

tidy_multi <- broom::tidy(
  mod_multi,
  conf.int = TRUE,
  conf.level = 0.95,
)

tidy_multi = tidy_multi %>% mutate(
    OR      = round(exp(estimate), 3),
    CI_low  = round(exp(conf.low), 3),
    CI_high = round(exp(conf.high), 3),
    p.value = round(p.value, 3),
    formatted = sprintf(
      "%.3f [%.3f, %.3f]",
      OR, CI_low, CI_high, p.value
    )
  )
tidy_multi %>% 
  select(y.level, formatted, OR, CI_low, CI_high, p.value, term) %>% 
  filter(term == "groupxDex") %>%
  arrange(y.level)
```

## mortality in ICU
```{r}
# mortality_in_icu
mod1 <- glm(mortality_in_icu ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod1,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "Mortality in ICU")
```
## mortality in hospital
```{r}
tdata2$mortality_in_hosp %>% table()

# mortality_in_hosp
mod3 <- glm(mortality_in_hosp ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod3,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "mortality_in_hosp")
```

## days from enrollment to death
```{r}
tdata2$enroll_death_days = round(tdata2$enroll_death_days,0)
# days_enroll_death
mod_e_d_days <- MASS::glm.nb(enroll_death_days ~ groupx, tdata2)
tbl_regression(
  mod_e_d_days,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "days_enroll_death")
```
## days from first drug to death
```{r}
tdata2$first_drug_death_days = round(tdata2$first_drug_death_days,0)
# first drug death days
mod_fd_d_days <- MASS::glm.nb(first_drug_death_days ~ groupx, tdata2)
tbl_regression(
  mod_fd_d_days,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "first_drug_death_days")
```

## mortality within 14 days from enrollment
```{r}
# mortality_within_14d_from_date_enrolled
mod2 <- glm(mortality_within_14d_from_date_enrolled ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod2,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "mortality_within_14d_from_date_enrolled")
```

## mortality within 14 days from first study drug admin
```{r}
# mortality_within_14d_from_date_enrolled
mod2 <- glm(mortality_within_14d_from_first_med_adm ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod2,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "mortality_within_14d_from_first_med_adm")
```

## mortality within 12 months from enrollment
```{r}
# mortality_within_12_months_from_date_enrolled
mod4 <- glm(mortality_within_12_months_from_date_enrolled ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod4,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "mortality_within_12_months_from_date_enrolled")
```

## readmission 30-day
```{r}
table(tdata2$readmit_30d_discharge)
mod_readmit <- glm(readmit_30d_discharge ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod_readmit,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "readmit_30d_discharge")
```

```{r}
# histogram data for these 4 variables
hist_data = tdata2 %>%
  select(sid,groupx ,survival_days_in_icu, survival_days_in_hosp, adj_in_hosp_coma_days, adj_icu_coma_days)
clipr::write_clip(hist_data)

# additional checks

#hist(tdata2$adj_in_hosp_coma_days)
#table(tdata2$adj_in_hosp_coma_days)
#hist(tdata2$adj_icu_coma_days)
#table(tdata2$adj_icu_coma_days)

# no point to run the first two due to limited numbers of events, but we can run the last two

# # survival_days_in_icu
# mod5 <- lm(survival_days_in_icu ~ group2, tdata2)
# tbl_regression(
#   mod5,
#   estimate_fun = ~ style_number(.x, digits = 3),
#   pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
#   as_gt() %>%
#   gt::tab_header(title = "survival_days_in_icu")
# 
# # survival_days_in_hosp
# mod6 <- lm(survival_days_in_hosp ~ group2, tdata2)
# tbl_regression(
#   mod6,
#   estimate_fun = ~ style_number(.x, digits = 3),
#   pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
#   as_gt() %>%
#   gt::tab_header(title = "survival_days_in_hosp")
```

## medication models
```{r}
# med_duringstudy_opioids_yn
mod9 <- glm(med_duringstudy_opioids_yn ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod9,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "Opioids during study (Y/N)")

# med_duringstudy_benzos_yn
mod10 <- glm(med_duringstudy_benzos_yn ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod10,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "Benzodiazepines during study (Y/N)")

# "med_duringstudy_phenobarbital_yn"
mod11 <- glm(med_duringstudy_phenobarbital_yn ~ groupx, tdata2, family = binomial)
tbl_regression(
  mod11,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)) %>%
  as_gt() %>%
  gt::tab_header(title = "Phenobarbital during study (Y/N)")

# "med_duringstudy_chlordiazepoxide_yn", 
mod_chlordiazepoxide <- glm(
  med_duringstudy_chlordiazepoxide_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_chlordiazepoxide <- tbl_regression(
  mod_chlordiazepoxide,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("chlordiazepoxide during study (Y/N): Odds Ratios")
  )

tbl_chlordiazepoxide

# "med_duringstudy_antipsychotics_yn", 
mod_antipsychotics <- glm(
  med_duringstudy_antipsychotics_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_antipsychotics <- tbl_regression(
  mod_antipsychotics,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("antipsychotics during study (Y/N): Odds Ratios")
  )

tbl_antipsychotics

# "med_duringstudy_propofol_yn", 
mod_propofol <- glm(
  med_duringstudy_propofol_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_propofol <- tbl_regression(
  mod_propofol,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("propofol during study (Y/N): Odds Ratios")
  )

tbl_propofol

# "med_duringstudy_ketamine_yn", 
mod_ketamine <- glm(
  med_duringstudy_ketamine_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_ketamine <- tbl_regression(
  mod_ketamine,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("ketamine during study (Y/N): Odds Ratios")
  )

tbl_ketamine

# "med_duringstudy_dexmedetomidine_yn", 
mod_dexmedetomidine <- glm(
  med_duringstudy_dexmedetomidine_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_dexmedetomidine <- tbl_regression(
  mod_dexmedetomidine,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("dexmedetomidine during study (Y/N): Odds Ratios")
  )

tbl_dexmedetomidine

# "med_duringstudy_melatonin_yn"
mod_melatonin <- glm(
  med_duringstudy_melatonin_yn ~ groupx,
  data = tdata2,
  family = binomial
)

tbl_melatonin <- tbl_regression(
  mod_melatonin,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(
    title = md("melatonin during study (Y/N): Odds Ratios")
  )

tbl_melatonin
```

## adj_in_hosp_coma_days
```{r}
# adj_in_hosp_coma_days --> imputed hospital coma days
# multinomial model
library(ordinal)
mod7 <- clm(adj_in_hosp_coma_days_cat ~ groupx, data = tdata2, link = "logit")
# run brant test to check proportional odds assumption
# gofcat::brant.test(mod7)
# scale_test(mod7)

tbl_mod7 <- tbl_regression(
  mod7,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(title = "imputed hospital coma days (clm logit ORs)")

tbl_mod7
```

## adj_icu_coma_days
```{r}
# adj_icu_coma_days --> imputed icu coma days
mod8 <- clm(adj_icu_coma_days_cat ~ groupx, data = tdata2, link = "logit")
# run brant test to check proportional odds assumption
# gofcat::brant.test(mod8)
# scale_test(mod8)

tbl_mod8 <- tbl_regression(
  mod8,
  exponentiate = TRUE,
  estimate_fun = ~ style_number(.x, digits = 3),
  pvalue_fun   = ~ style_pvalue(.x, digits = 3)
) %>%
  as_gt() %>%
  gt::tab_header(title = "imputed icu coma days (clm logit ORs)")
tbl_mod8
```









