---
title: "Primary Analysis"
output: 
  html_notebook: 
    toc: true
    toc_depth: 4
    toc_float: true
    theme: simplex
    number_sections: true
    highlight: zenburn
    fig_width: 8
    fig_height: 6
    css: custom.css
---

```{r warning=FALSE , message=FALSE}
rm(list = ls())
library(tidyverse)
library(tableone)
library(openxlsx)
library(knitr)
library(magrittr)
library(janitor)
library(readxl)
options(scipen=999)
library(readr)
library(gofcat)

# set width of the output
options(width = 120)
```

# Load data
```{r}
outcome1 = readRDS("data/rds/outcome1.rds")
group = readRDS("data/rds/group.rds")
demo = readRDS("data/rds/demo.rds")
itt = readRDS("data/rds/itt.rds")
# sanity check: itt group does not contain keyword bolus
# itt = itt %>% filter(randomization_allocation_assignment_list %in% c("Dex 0.1 mcg/kg/h", "Dex 0.3 mcg/kg/h", "Placebo"))
# pp = readRDS("data/rds/pp.rds")
mitt = readRDS("data/rds/mitt.rds")
adj = demo %>% select(sid, age, sex, race, ethnicity)
```

# Apply analytical samples
```{r}
# use mitt
outcome1 = outcome1 %>% filter(sid %in% mitt$sid)
group = group %>% filter(sid %in% mitt$sid)

# group2g to combine two Dex groups
group$group2g = group$group %>% as.character()
group$group2g[group$group2g == "Dex 0.1 mcg/kg/h"] = "Dex"
group$group2g[group$group2g == "Dex 0.3 mcg/kg/h"] = "Dex"
group$group2g = as.character(group$group2g)
group$group2g = as.factor(group$group2g)
group$group2g = relevel(group$group2g, ref = "Placebo")

# set Placebo as the group reference
group$group3g = group$group %>% as.character()
group$group3g = as.factor(group$group3g)
group$group3g = relevel(group$group3g, ref = "Placebo")

# remove group
group = group %>% select(-group)

# left join
data1 = left_join(outcome1, group, by = "sid")
data1 = left_join(data1, adj, by = "sid")
data1 = data1 %>% filter(sid %in% mitt$sid)
```

```{r}
# adj_14day_DFD is the imputed DFD for in-hospital DFDs -> up to 14 days.

# make adj_14day_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_DFDs) %>% sort()
data1$adj_DFDs = factor(data1$adj_DFDs, levels = levels, ordered = T)

# make unadj_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_DFDs) %>% sort()
data1$unadj_DFDs = factor(data1$unadj_DFDs, levels = levels, ordered = T)

# make adj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_ICU_DFDs) %>% sort()
data1$adj_ICU_DFDs = factor(data1$adj_ICU_DFDs, levels = levels, ordered = T)

# make unadj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_ICU_DFDs) %>% sort()
data1$unadj_ICU_DFDs = factor(data1$unadj_ICU_DFDs, levels = levels, ordered = T)

#janitor::tabyl(outcome1$adj_DFDs)
#janitor::tabyl(outcome1$unadj_DFDs)

covariate = demo %>% 
  select(sid, day_1_sofa_score, mean_iqcode_score, delirium_status,days_in_icu_pre_enrollment, days_in_hosp_pre_enrollment,obstructive_sleep_apnea_y_n,
         med_prestudy_benzos_yn,med_prestudy_phenobarbital_yn)
  
data1 = left_join(data1, covariate, by = "sid")
```

```{r}
# data1$delirium_status as 0/1
data1$delirium_status = case_when(
  data1$delirium_status == "N" ~ 0,
  data1$delirium_status == "Y" ~ 1
)

data1 = data1 %>% mutate(t_icu = days_in_icu_pre_enrollment) # t_icu --> days in ICU pre-enrollment
data1 = data1 %>% mutate(t_hosp = days_in_hosp_pre_enrollment) # t_hosp --> days in hospital pre-enrollment
```

# choose 2 groups or 3 groups

Now we start analysis - distributions already checked up
- primary analysis start here
- groupx is group2g or group3g depending on the selection

```{r}
# now new group2 = 2g or 3g
# data1 = data1 %>% mutate(groupx = group2g)
data1 = data1 %>% mutate(groupx = group3g)
```

```{r}
library(clipr)
# check distribution of DFDs
dist_plot_data = data1 %>% select(sid, group2g, group3g, adj_DFDs, unadj_DFDs, adj_ICU_DFDs, unadj_ICU_DFDs)
write_clip(dist_plot_data)
```

```{r}
data1$adj_DFDs <- ordered(data1$adj_DFDs)
data1$unadj_DFDs <- ordered(data1$unadj_DFDs)
data1$adj_ICU_DFDs <- ordered(data1$adj_ICU_DFDs)
data1$unadj_ICU_DFDs <- ordered(data1$unadj_ICU_DFDs)
```



# Imputed in-hosp DFDs
Note: adj in-hosp DFDs are calculated as imputed upto 14-day DFD.

## crude/univariate
```{r}
library(ordinal)
library(gtsummary)                                                
# load each session

# crude model
mod1 = clm(adj_DFDs ~ groupx, data = data1, link = "logit")
summary(mod1)
# tests
# brant.test(mod1)
# scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

## multivariable model
```{r fig.height=6, fig.width=12}
library(performance)

# adjusted model
adjust = " + age + day_1_sofa_score + mean_iqcode_score + delirium_status + t_hosp + t_icu"
fit1 = paste0("adj_DFDs", " ~ groupx", adjust)
fit1
mod1 = clm(fit1, data = data1, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))

```
## interaction analysis for mv model
- groupx*delirium_status interaction
```{r}
# interaction analysis
# adjusted model
fit1 = "adj_DFDs ~ groupx*delirium_status + age + day_1_sofa_score + mean_iqcode_score + t_icu + t_hosp"
mod1 = clm(fit1, data = data1, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

## compare models
conclusion: the interaction model did not significantly improve model fit -> go with mv model without interaction term.
```{r}
# compare models: uni vs mv vs interaction -> LR test
uni = clm(adj_DFDs ~ groupx, data = data1, link = "logit")
mv = clm(adj_DFDs ~ groupx + age + mean_iqcode_score + delirium_status + t_icu + t_hosp, data = data1, link = "logit")
interaction = clm(adj_DFDs ~ groupx*delirium_status + age + mean_iqcode_score + t_icu + t_hosp, data = data1, link = "logit")
anova(uni, mv)
anova(mv, interaction)
```

# Unimputed in-hosp DFDs
## crude model
```{r}
# crude model
fit1 = paste0("unadj_DFDs", " ~ groupx")
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))


```
## multivariable model
```{r fig.height=6, fig.width=12}
library(performance)
# adjusted model
adjust = " + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp"
fit1 = paste0("unadj_DFDs", " ~ groupx", adjust)
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

# Imputed in-ICU DFDs
## crude
```{r}
# crude model
fit1 = paste0("adj_ICU_DFDs", " ~ groupx") # imputed ICU DFDs
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```
## multivariate model
```{r fig.height=6, fig.width=12}
library(performance)

# adjusted model
adjust = " + age + day_1_sofa_score + mean_iqcode_score + delirium_status + t_hosp + t_icu"

fit1 = paste0("adj_ICU_DFDs", " ~ groupx", adjust)
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))

```
## interaction analysis for MV model
```{r}
# interaction analysis
# adjusted model
fit1 = "adj_ICU_DFDs ~ groupx*delirium_status + age + day_1_sofa_score + mean_iqcode_score + t_icu + t_hosp"
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
library(emmeans)
emm1 = emmeans(mod1, list(pairwise ~ groupx|delirium_status))
summary(emm1, infer = T, adjust = "none")
```

## compare models
conclusion: same as in-hosp DFDs, the interaction model did not significantly improve model fit -> go with mv model without interaction
```{r}
# compare models: uni vs mv vs interaction -> LR test
uni = clm(adj_ICU_DFDs ~ groupx, data = data1, link = "logit", method = "nlminb")
mv = clm(adj_ICU_DFDs ~ groupx + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, data = data1, link = "logit", method = "nlminb")
interaction = clm(adj_ICU_DFDs ~ groupx*delirium_status + age + day_1_sofa_score + mean_iqcode_score + t_icu + t_hosp, data = data1, link = "logit", method = "nlminb")
anova(uni, mv)
anova(mv, interaction)
```
# Unimputed in-ICU DFDs
## crude
```{r}
# crude model
fit1 =  NULL 
fit1 = paste0("unadj_ICU_DFDs", " ~ groupx") # unimputed ICU DFDs
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```
## mv model
```{r fig.height=6, fig.width=12}
library(performance)
# adjusted model
adjust = " + age + day_1_sofa_score + mean_iqcode_score + delirium_status + t_icu + t_hosp"
fit1 = paste0("unadj_ICU_DFDs", " ~ groupx", adjust)
mod1 = clm(fit1, data = data1, link = "logit", method = "nlminb")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

# HTE analysis
## Imputed in-hosp DFDs
```{r}
# HTE analysis for in-hosp DFDs
# make adj_DFDs a binary variable: 0 if DFDs >7, 1 if DFDs <= 7
data1$adj_DFDs2 = as.numeric(as.character(data1$adj_DFDs))
data1$adj_DFDs2 = case_when(
  data1$adj_DFDs2 > 7 ~ 0,
  data1$adj_DFDs2 <= 7 ~ 1
)

# table(data1$adj_DFDs2)

risk_fit <- glm(
  adj_DFDs2 ~ age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,
  family = binomial(),
  data = data1
)

# risk_fit <- glm(
#   adj_DFDs2 ~ age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,
#   family = binomial(),
#   data = subset(data1, groupx == "Placebo")
# )
# summary(risk_fit)

data1$risk0 <- predict(risk_fit, newdata = data1, type = "response")
summary(data1$risk0)
```

```{r}
hte_fit <- glm(
  adj_DFDs2 ~ groupx * risk0,
  family = binomial(),
  data = data1
)
```

```{r}
# Install if needed:
# install.packages(c("fastshap", "ggplot2", "dplyr", "tidyr"))

library(fastshap)
library(ggplot2)
library(dplyr)
library(tidyr)

# --------------------------------------------------
#   Predictor matrix for SHAP
# --------------------------------------------------
X <- data1 %>%
  select(
    age,
    mean_iqcode_score,
    day_1_sofa_score,
    delirium_status,
    t_icu,
    t_hosp
  )

# --------------------------------------------------
#    Prediction wrapper
#    Explain the model on the log-odds scale
# --------------------------------------------------
pred_wrapper_link <- function(object, newdata) {
  out <- predict(object, newdata = newdata, type = "link")
  unname(as.numeric(out))
}

# Sanity check
tmp <- pred_wrapper_link(risk_fit, X)
stopifnot(is.numeric(tmp), length(tmp) == nrow(X))

# --------------------------------------------------
# Compute SHAP values
# --------------------------------------------------
set.seed(123)

shap_values <- fastshap::explain(
  object = risk_fit,
  X = X,
  pred_wrapper = pred_wrapper_link,
  nsim = 200,
  adjust = TRUE
)

# --------------------------------------------------
# Global SHAP importance
# --------------------------------------------------
global_shap <- data.frame(
  feature = colnames(shap_values),
  mean_abs_shap = apply(abs(as.matrix(shap_values)), 2, mean)
) %>%
  arrange(desc(mean_abs_shap))

# relabel features
global_shap$feature <- recode(global_shap$feature,
  age = "Age",
  mean_iqcode_score = "Mean IQCODE Score",
  day_1_sofa_score = "Day 1 SOFA Score",
  delirium_status = "Delirium Status",
  t_icu = "Days in ICU Pre-enrollment",
  t_hosp = "Days in Hospital Pre-enrollment"
)

# remove rownames
rownames(global_shap) <- NULL

print(global_shap)
clipr::write_clip(global_shap)
```

```{r}
library(dplyr)
library(ggplot2)
library(scales)

# make sure groupx is a factor
data1$groupx <- factor(data1$groupx)

# fit model
fit <- glm(
  adj_DFDs2 ~ groupx * risk0,
  family = binomial(),
  data = data1
)

# levels of current groupx
levs <- levels(data1$groupx)

# grid of baseline risk
grid <- data.frame(
  risk0 = seq(
    quantile(data1$risk0, 0.01, na.rm = TRUE),
    quantile(data1$risk0, 0.99, na.rm = TRUE),
    length.out = 200
  )
)

invlogit <- function(x) 1 / (1 + exp(-x))

# predicted curves for all levels of groupx
plot_list <- lapply(levs, function(g) {
  newdat <- grid
  newdat$groupx <- factor(g, levels = levs)

  pred <- predict(fit, newdata = newdat, type = "link", se.fit = TRUE)

  data.frame(
    risk0 = grid$risk0,
    group = g,
    fit = invlogit(pred$fit),
    lo  = invlogit(pred$fit - 1.96 * pred$se.fit),
    hi  = invlogit(pred$fit + 1.96 * pred$se.fit)
  )
})

plot_dat <- bind_rows(plot_list)

# turn long format data to wide format
plot_dat_wide <- plot_dat %>%
  pivot_wider(
    id_cols = risk0,
    names_from = group,
    values_from = c(fit, lo, hi),
    names_sep = "_"
  )

plot_dat_wide
clipr::write_clip(plot_dat_wide)
```

```{r fig.height=5, fig.width=6}
library(ggprism)
my_cols <- c(
  "Placebo" = "#d62728",
  "Dex" = "#1f77b4",
  "Dex 0.1 mcg/kg/h" = "#1f77b4",
  "Dex 0.3 mcg/kg/h" = "darkgreen"
)

ggplot(plot_dat, aes(x = risk0, y = fit, color = group, fill = group)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.12, color = NA) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = my_cols) +
  scale_fill_manual(values = my_cols) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.1),
    labels = percent_format(accuracy = 1)
  ) +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2),
    limits = c(0, 1),
    labels = percent_format(accuracy = 1)
  ) +
  labs(
    x = "Predicted baseline risk",
    y = "Predicted probability of poor DFD outcome",
    color = NULL,
    linetype = NULL,
    fill = NULL
  ) +
  theme_prism(base_size = 12) +
  theme(legend.position = "top") + 
  ggtitle("Heterogeneity of treatment effect for in-hospital DFDs")
```
## Imputed ICU DFDs
```{r}
# HTE analysis for in-hosp DFDs
# make adj_DFDs a binary variable: 0 if DFDs >7, 1 if DFDs <= 7
data1$adj_ICU_DFDs2 = as.numeric(as.character(data1$adj_ICU_DFDs))
data1$adj_ICU_DFDs2 = case_when(
  data1$adj_ICU_DFDs2 > 3 ~ 0,
  data1$adj_ICU_DFDs2 <= 3 ~ 1
)


risk_fit <- glm(
  adj_ICU_DFDs2 ~ age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,
  family = binomial(),
  data = data1
)
summary(risk_fit)

# table(data1$adj_DFDs2)
# risk_fit <- glm(
#   adj_ICU_DFDs2 ~ age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,
#   family = binomial(),
#   data = subset(data1, groupx == "Placebo")
# )
# summary(risk_fit)

data1$risk0 <- predict(risk_fit, newdata = data1, type = "response")
summary(data1$risk0)
```

```{r}
hte_fit <- glm(
  adj_ICU_DFDs2 ~ groupx * risk0,
  family = binomial(),
  data = data1
)
```

```{r}
# Install if needed:
# install.packages(c("fastshap", "ggplot2", "dplyr", "tidyr"))

library(fastshap)
library(ggplot2)
library(dplyr)
library(tidyr)

# --------------------------------------------------
#   Predictor matrix for SHAP
# --------------------------------------------------
X <- data1 %>%
  select(
    age,
    mean_iqcode_score,
    day_1_sofa_score,
    delirium_status,
    t_icu,
    t_hosp
  )

# --------------------------------------------------
#    Prediction wrapper
#    Explain the model on the log-odds scale
# --------------------------------------------------
pred_wrapper_link <- function(object, newdata) {
  out <- predict(object, newdata = newdata, type = "link")
  unname(as.numeric(out))
}

# Sanity check
tmp <- pred_wrapper_link(risk_fit, X)
stopifnot(is.numeric(tmp), length(tmp) == nrow(X))

# --------------------------------------------------
# Compute SHAP values
# --------------------------------------------------
set.seed(123)

shap_values <- fastshap::explain(
  object = risk_fit,
  X = X,
  pred_wrapper = pred_wrapper_link,
  nsim = 200,
  adjust = TRUE
)

# --------------------------------------------------
# Global SHAP importance
# --------------------------------------------------
global_shap <- data.frame(
  feature = colnames(shap_values),
  mean_abs_shap = apply(abs(as.matrix(shap_values)), 2, mean)
) %>%
  arrange(desc(mean_abs_shap))

# relabel features
global_shap$feature <- recode(global_shap$feature,
  age = "Age",
  mean_iqcode_score = "Mean IQCODE Score",
  day_1_sofa_score = "Day 1 SOFA Score",
  delirium_status = "Delirium Status",
  t_icu = "Days in ICU Pre-enrollment",
  t_hosp = "Days in Hospital Pre-enrollment"
)

# remove rownames
rownames(global_shap) <- NULL

print(global_shap)
clipr::write_clip(global_shap)
```

```{r}
library(dplyr)
library(ggplot2)
library(scales)

# make sure groupx is a factor
data1$groupx <- factor(data1$groupx)

# fit model
fit <- glm(
  adj_ICU_DFDs2 ~ groupx * risk0,
  family = binomial(),
  data = data1
)

# levels of current groupx
levs <- levels(data1$groupx)

# grid of baseline risk
grid <- data.frame(
  risk0 = seq(
    quantile(data1$risk0, 0.01, na.rm = TRUE),
    quantile(data1$risk0, 0.99, na.rm = TRUE),
    length.out = 200
  )
)

invlogit <- function(x) 1 / (1 + exp(-x))

# predicted curves for all levels of groupx
plot_list <- lapply(levs, function(g) {
  newdat <- grid
  newdat$groupx <- factor(g, levels = levs)

  pred <- predict(fit, newdata = newdat, type = "link", se.fit = TRUE)

  data.frame(
    risk0 = grid$risk0,
    group = g,
    fit = invlogit(pred$fit),
    lo  = invlogit(pred$fit - 1.96 * pred$se.fit),
    hi  = invlogit(pred$fit + 1.96 * pred$se.fit)
  )
})

plot_dat <- bind_rows(plot_list)

# turn long format data to wide format
plot_dat_wide <- plot_dat %>%
  pivot_wider(
    id_cols = risk0,
    names_from = group,
    values_from = c(fit, lo, hi),
    names_sep = "_"
  )

plot_dat_wide
clipr::write_clip(plot_dat_wide)
```

```{r fig.height=5, fig.width=6}
my_cols <- c(
  "Placebo" = "#d62728",
  "Dex" = "#1f77b4",
  "Dex 0.1 mcg/kg/h" = "#1f77b4",
  "Dex 0.3 mcg/kg/h" = "darkgreen"
)

ggplot(plot_dat, aes(x = risk0, y = fit, color = group, fill = group)) +
  geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.12, color = NA) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = my_cols) +
  scale_fill_manual(values = my_cols) +
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.1),
    labels = percent_format(accuracy = 1)
  ) +
  scale_y_continuous(
    breaks = seq(0, 1, by = 0.2),
    limits = c(0, 1),
    labels = percent_format(accuracy = 1)
  ) +
  labs(
    x = "Predicted baseline risk",
    y = "Predicted probability of poor DFD outcome",
    color = NULL,
    linetype = NULL,
    fill = NULL
  ) +
  theme_prism(base_size = 12) +
  theme(legend.position = "top") + 
  ggtitle("Heterogeneity of treatment effect for ICU DFDs")
```


