---
title: "Survival Analysis"
output: 
  html_notebook: 
    toc: true
    toc_depth: 4
    toc_float: true
    theme: simplex
    number_sections: true
    highlight: zenburn
    fig_width: 8
    fig_height: 6
    css: custom.css
---

```{r warning=FALSE , message=FALSE}
rm(list = ls())
library(tidyverse)
library(tableone)
library(openxlsx)
library(knitr)
library(magrittr)
library(janitor)
library(readxl)
options(scipen=999)
library(readr)

# set width of the output
options(width = 120)
```

# Load data
```{r}
surv1 = readRDS("data/rds/surv1.rds")
group = readRDS("data/rds/group.rds")
demo = readRDS("data/rds/demo.rds")
itt = readRDS("data/rds/itt.rds")
# itt group does not contain keyword bolus
itt = itt %>% filter(randomization_allocation_assignment_list %in% c("Dex 0.1 mcg/kg/h", "Dex 0.3 mcg/kg/h", "Placebo"))
mitt = readRDS("data/rds/mitt.rds")
pp = readRDS("data/rds/pp.rds")
adj = demo %>% select(sid, age, sex, race, ethnicity)
```

# Apply analytical samples
```{r}
# use mitt
surv1 = surv1 %>% filter(sid %in% mitt$sid)
group = group %>% filter(sid %in% mitt$sid)
# group2 to combine two Dex groups
group$group2 = group$group %>% as.character()
group$group2[group$group2 == "Dex 0.1 mcg/kg/h"] = "Dex"
group$group2[group$group2 == "Dex 0.3 mcg/kg/h"] = "Dex"
group$group2 = as.character(group$group2)


# left join
data1 = left_join(surv1, group, by = "sid")
data1 = left_join(data1, adj, by = "sid")
data1 = data1 %>% filter(sid %in% mitt$sid)
```

```{r}
# set Placebo as the group reference
data1$group = factor(data1$group)
data1$group = relevel(data1$group, ref = "Placebo")

data1$group2 = as.factor(data1$group2)
data1$group2 = relevel(data1$group2, ref = "Placebo")

#janitor::tabyl(outcome1$adj_DFDs)
#janitor::tabyl(outcome1$unadj_DFDs)

covariate = demo %>% 
  select(sid, day_1_sofa_score, mean_iqcode_score, delirium_status,days_in_icu_pre_enrollment, days_in_hosp_pre_enrollment,obstructive_sleep_apnea_y_n,
         med_prestudy_benzos_yn,med_prestudy_phenobarbital_yn)
  
data1 = left_join(data1, covariate, by = "sid")
```

```{r}
# data1$delirium_status as 0/1
data1$delirium_status = case_when(
  data1$delirium_status == "N" ~ 0,
  data1$delirium_status == "Y" ~ 1
)

```

```{r}
data1 = data1 %>% mutate(t_icu = days_in_icu_pre_enrollment)
data1 = data1 %>% mutate(t_hosp = days_in_hosp_pre_enrollment)
```

```{r}
# data1 - mean_iqcode_score is centered around 3 and very small sd, normalize it
data1 <- data1 %>% mutate(mean_iqcode_score_z = as.numeric(scale(mean_iqcode_score)))
```

```{r}
# this is settup group variables not important
group = group %>% mutate(group3g = group, group2g = group2, groupx = group)
# set group now
group = group %>% select(-group, -group2)
# in group now we only have groupx, which is different
group$groupx = group$group2g
#group$groupx = group$group3g
```
# choose 2 groups or 3 groups
```{r}
data1$group_2g = data1$group2
data1$group_3g = data1$group
data1 = data1 %>% select(-group2, -group)

# now new groupx = 2g or 3g
# data1 = data1 %>% mutate(groupx = group_2g)
data1 = data1 %>% mutate(groupx = group_3g)

adjust = " + age + mean_iqcode_score + delirium_status + t_icu + t_hosp"
data1 = data1 %>% select(-group_2g,-group_3g)
```


Now we start analysis - distributions already checked up
- primary analysis start here
- group2 is group2g or group3g depending on the selection


# DID datetime standardization
```{r}
# note: surv1 datatime fields were all standardized to a fake enrollment date.
```

# check dataset
```{r}
library(skimr)
# glimpse(data1, width = 30)
```


```{r}
pkgs <- c("tidyverse","lubridate","survival","ggsurvfit","broom","gtsummary", "survminer")
invisible(lapply(setdiff(pkgs, rownames(installed.packages())), install.packages))
invisible(lapply(pkgs, library, character.only = TRUE))
```

```{r}
# ---- Hard QC: death cannot precede any known admission date ----
qc_bad <- data1 %>%
  filter(
    (!is.na(death_date) & !is.na(hosp_admission_dts) & death_date < hosp_admission_dts) |
    (!is.na(death_date) & !is.na(icu_admission_dts)  & death_date < icu_admission_dts)
  ) %>%
  select(sid, hosp_admission_dts, icu_admission_dts, death_date)

if (nrow(qc_bad) > 0) {
  print(qc_bad)
  stop(sprintf("QC failed: %d rows have death_date earlier than admission. Fix these before analysis.", nrow(qc_bad)))
}
```

# QA
```{r}
# set up dataset: add day14 cut to data but it's all data
data1_14d <- data1 %>%
  select(sid, groupx,
         date_sda = date_time_first_study_drug_administration,
         # date_enrolled, # we use date sda for calculation
         death_date, 
         age, mean_iqcode_score_z, delirium_status, t_icu, t_hosp, day_1_sofa_score,
         icu_discharge_dts,hosp_discharge_dts) %>%
  mutate(surv_raw_days = as.numeric(death_date - date_sda, units = "days"),
         day14 = date_sda + days(14),
         days_to_icu_discharge = as.numeric(icu_discharge_dts - date_sda, units = "days"),
         days_to_hosp_discharge = as.numeric(hosp_discharge_dts - date_sda, units = "days")
         )

# how many death
data1_14d %>% filter(!is.na(death_date)) %>% nrow()
# how many death within 14 days
data1_14d %>% filter(!is.na(death_date) & death_date < date_sda + days(14)) %>% nrow()
# who died at between day 14 and day 15
data1_14d %>% filter(!is.na(death_date) & death_date > date_sda + days(14) & death_date < date_sda + days(15)) %>% nrow()
# x = data1_14d %>% filter(!is.na(death_date) & death_date > date_sda + days(14) & death_date <= date_sda + days(15))

data1_death = data1_14d %>% filter(!is.na(death_date) & death_date < date_sda + days(14))

# how many deaths within icu
data1_death %>% filter(!is.na(death_date) & !is.na(icu_discharge_dts) & death_date <= icu_discharge_dts) %>% nrow()
# x = data1_death %>% filter(!is.na(death_date) & !is.na(icu_discharge_dts) & death_date <= icu_discharge_dts)

# how many died within 7 days but outside of icu
data1_death %>% filter(death_date > icu_discharge_dts & death_date <= date_sda + days(7)) %>% nrow()

# how many died within hospital
data1_death %>% filter(!is.na(death_date) & !is.na(hosp_discharge_dts) & death_date <= hosp_discharge_dts) %>% nrow()

# how many died within 14 days but outside of hospital
data1_death %>% filter(death_date > hosp_discharge_dts & death_date <= date_sda + days(14)) %>% nrow()
```
# death plot
```{r}
# install if needed
if (!requireNamespace("ggsci", quietly = TRUE)) install.packages("ggsci")
if (!requireNamespace("ggprism", quietly = TRUE)) install.packages("ggprism")
library(ggsci)
library(ggprism)
```

```{r}
library(clipr)
# data1_14day has all mITT patients. rename to data2
data2 = data1_14d
data_icu_death = data2 %>% filter(!is.na(death_date) & !is.na(icu_discharge_dts) & death_date <= icu_discharge_dts)
data_hosp_death = data2 %>% filter(!is.na(death_date) & !is.na(hosp_discharge_dts) & death_date <= hosp_discharge_dts)
```

# in hospital death plot data - 2g
```{r}
# calculate culmulative death sum of data_hosp_death
hosp_death = data_hosp_death %>% select(sid, surv_raw_days, groupx) %>% arrange(surv_raw_days)
days_dex <- hosp_death %>% filter(groupx == "Dex") %>% pull(surv_raw_days)
day_placebo <- hosp_death %>% filter(groupx == "Placebo") %>% pull(surv_raw_days)
max_day <- max(c(days_dex, day_placebo), na.rm = TRUE) %>% ceiling()
# define the range of interest
day_range <- 0:25
# compute cumulative count at each day
dex = cum_counts <- sapply(day_range, function(d) sum(days_dex <= d))
placebo = cum_counts <- sapply(day_range, function(d) sum(day_placebo <= d))
# combine into a data frame
df_dex <- data.frame(day = day_range, cumulative_count = dex, group = "Dex")
df_placebo <- data.frame(day = day_range, cumulative_count = placebo, group = "Placebo")
df = rbind(df_dex, df_placebo)

df_plot_wide = df %>% pivot_wider(names_from = group, values_from = cumulative_count) %>% arrange(day)
write_clip(df_plot_wide) # copy to clipboard for datagraph plots
```

# in hospital death plot data - 3g
```{r}
# calculate culmulative death sum of data_hosp_death
hosp_death = data_hosp_death %>% select(sid, surv_raw_days, groupx) %>% arrange(surv_raw_days)
days_dex1 <- hosp_death %>% filter(groupx == "Dex 0.1 mcg/kg/h") %>% pull(surv_raw_days)
days_dex2 <- hosp_death %>% filter(groupx == "Dex 0.3 mcg/kg/h") %>% pull(surv_raw_days)
day_placebo <- hosp_death %>% filter(groupx == "Placebo") %>% pull(surv_raw_days)
max_day <- max(c(days_dex1,days_dex2, day_placebo), na.rm = TRUE) %>% ceiling()
# define the range of interest
day_range <- 0:25
# compute cumulative count at each day
dex1 = cum_counts <- sapply(day_range, function(d) sum(days_dex1 <= d))
dex2 = cum_counts <- sapply(day_range, function(d) sum(days_dex2 <= d))
placebo = cum_counts <- sapply(day_range, function(d) sum(day_placebo <= d))
# combine into a data frame
df_dex1 <- data.frame(day = day_range, cumulative_count = dex1, group = "Dex 0.1 mcg/kg/h")
df_dex2 <- data.frame(day = day_range, cumulative_count = dex2, group = "Dex 0.3 mcg/kg/h")
df_placebo <- data.frame(day = day_range, cumulative_count = placebo, group = "Placebo")
df = rbind(df_dex1, df_dex2, df_placebo)

df_plot_wide = df %>% pivot_wider(names_from = group, values_from = cumulative_count) %>% arrange(day)
write_clip(df_plot_wide) # copy to clipboard for datagraph plots
```

# in ICU death plot data-2g
```{r}
# calculate culmulative death sum of data_icu_death
icu_death = data_icu_death %>% select(sid, surv_raw_days, groupx) %>% arrange(surv_raw_days)
days_dex <- icu_death %>% filter(groupx == "Dex") %>% pull(surv_raw_days)
day_placebo <- icu_death %>% filter(groupx == "Placebo") %>% pull(surv_raw_days)
max_day <- max(c(days_dex, day_placebo), na.rm = TRUE) %>% ceiling()
# define the range of interest
day_range <- 0:20
# compute cumulative count at each day
dex = cum_counts <- sapply(day_range, function(d) sum(days_dex <= d))
placebo = cum_counts <- sapply(day_range, function(d) sum(day_placebo <= d))
# combine into a data frame
df_dex <- data.frame(day = day_range, cumulative_count = dex, group = "Dex")
df_placebo <- data.frame(day = day_range, cumulative_count = placebo, group = "Placebo")
df = rbind(df_dex, df_placebo)

df_plot_wide = df %>% pivot_wider(names_from = group, values_from = cumulative_count) %>% arrange(day)
write_clip(df_plot_wide) # copy to clipboard for datagraph plots
```

# in ICU death plot data-3g
```{r}
# calculate culmulative death sum of data_icu_death
icu_death = data_icu_death %>% select(sid, surv_raw_days, groupx) %>% arrange(surv_raw_days)
days_dex1 <- icu_death %>% filter(groupx == "Dex 0.1 mcg/kg/h") %>% pull(surv_raw_days)
days_dex2 <- icu_death %>% filter(groupx == "Dex 0.3 mcg/kg/h") %>% pull(surv_raw_days)
day_placebo <- icu_death %>% filter(groupx == "Placebo") %>% pull(surv_raw_days)
max_day <- max(c(days_dex1,days_dex2, day_placebo), na.rm = TRUE) %>% ceiling()
# define the range of interest
day_range <- 0:20
# compute cumulative count at each day
dex1 = cum_counts <- sapply(day_range, function(d) sum(days_dex1 <= d))
dex2 = cum_counts <- sapply(day_range, function(d) sum(days_dex2 <= d))
placebo = cum_counts <- sapply(day_range, function(d) sum(day_placebo <= d))
# combine into a data frame
df_dex1 <- data.frame(day = day_range, cumulative_count = dex1, group = "Dex 0.1 mcg/kg/h")
df_dex2 <- data.frame(day = day_range, cumulative_count = dex2, group = "Dex 0.3 mcg/kg/h")
df_placebo <- data.frame(day = day_range, cumulative_count = placebo, group = "Placebo")
df = rbind(df_dex1, df_dex2, df_placebo)

df_plot_wide = df %>% pivot_wider(names_from = group, values_from = cumulative_count) %>% arrange(day)
write_clip(df_plot_wide) # copy to clipboard for datagraph plots
```

# survival analysis till day 30
Why?: almost all in-hospital and in-ICU death happen within 30 days. So it's more meaningful to look at survival curve within 30 days. 
```{r}
data3 = data1_14d

library(dplyr)
library(lubridate)

max_followup <- 30
data3_30d <- data3 %>%
  mutate(
    # Determine the censor/event date capped at 30 days
    surv_end_date = pmin(death_date, date_sda + days(max_followup), na.rm = TRUE),
    
    # Event: death occurs within 30 days
    event_30d = as.integer(!is.na(death_date) & death_date <= date_sda + days(max_followup)),
    
    # Time in days from enrollment to event/censor
    time_30d = as.numeric(surv_end_date - date_sda, units = "days")
  ) %>%
  filter(!is.na(time_30d) & time_30d >= 0)

# table(data3_30d$event_30d)
# summary(data3_30d$time_30d)
```


```{r}
data3_30d_death = data3_30d %>% filter(event_30d == 1)
# boxplot data of survival days by groupx
boxplot_data = data3_30d_death %>% select(groupx, time_30d)
boxplot_data_wide = boxplot_data %>% pivot_wider(names_from = groupx, values_from = time_30d)
write_clip(boxplot_data) # copy to clipboard for datagraph plots
```



```{r}
library(survival)

surv_obj_30d <- with(data3_30d, Surv(time_30d, event_30d))
km_fit_30d  <- survfit(surv_obj_30d ~ groupx, data = data3_30d)

# Inspect survival probabilities at selected times
summary(km_fit_30d, times = c(1, 3, 7, 14, 21, 28, 30))

# Test difference between groups
logrank_test = survdiff(surv_obj_30d ~ groupx, data = data3_30d)
print(logrank_test)

library(broom)
tidy_km <- broom::tidy(km_fit_30d)

# turn it into wide format by strata
tidy_km_wide <- tidy_km %>%
  select(strata, time, n.risk, n.event, n.censor, estimate,, conf.high, conf.low) %>%
  pivot_wider(names_from = strata, values_from = c(n.risk, n.event, estimate, conf.high, conf.low)) %>%
  arrange(time)
# copy
write_clip(tidy_km_wide) # copy to clipboard for datagraph plots
```


```{r}
cox_fit_30d <- coxph(surv_obj_30d ~ groupx + age + day_1_sofa_score + mean_iqcode_score_z + delirium_status + t_icu + t_hosp, data = data3_30d)
summary(cox_fit_30d)
```

```{r fig.height=8, fig.width=6}
library(survminer)
library(ggsci)
library(ggprism)

# Palette for groups
# manually green, blue, red for Dex 0.3, 0.1, placebo
palette_groups <- c("Dex" = "#0072B5FF","Dex 0.3 mcg/kg/h" = "#20854EFF", "Dex 0.1 mcg/kg/h" = "#0072B5FF", "Placebo" = "#BC3C29FF")
# palette_groups <- c( "Placebo" = "#BC3C29FF")

km_plot_30d <- ggsurvplot(
  km_fit_30d,
  data = data3_30d,
  conf.int = TRUE,
  risk.table = TRUE,
  censor = TRUE,
  palette = palette_groups,
  ggtheme = theme_minimal(),
  title = "",
  xlab = "Days since first study drug administration",
  ylab = "Survival probability",
  ylim = c(0.85, 1),
  xlim = c(0, max_followup),
  break.time.by = 7,
  risk.table.height = 0.22,
  risk.table.y.text = TRUE,
  risk.table.col = "black",
  legend.title = "",
  legend.labs = levels(data3_30d$groupx)
)

# Style the survival curve panel
km_plot_30d$plot <- km_plot_30d$plot +
  ggprism::theme_prism(base_size = 12) +
  theme(
    legend.position = "top",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  geom_vline(xintercept = c(7, 14, 21, 28),
             linetype = "dotted", linewidth = 0.6, color = "grey30")

# Style the risk table
km_plot_30d$table <- km_plot_30d$table +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

print(km_plot_30d)
```







