---
title: "Sensitivity Analysis"
output: 
  html_notebook: 
    toc: true
    toc_depth: 4
    toc_float: true
    theme: simplex
    number_sections: true
    highlight: zenburn
    fig_width: 8
    fig_height: 6
    css: custom.css
---

```{r warning=FALSE , message=FALSE}
rm(list = ls())
library(tidyverse)
library(tableone)
library(openxlsx)
library(knitr)
library(magrittr)
library(janitor)
library(readxl)
options(scipen=999)
library(readr)
library(gofcat)

# set width of the output
options(width = 120)
```

# Load data
```{r}
outcome1 = readRDS("data/rds/outcome1.rds")
group = readRDS("data/rds/group.rds")
demo = readRDS("data/rds/demo.rds")
itt = readRDS("data/rds/itt.rds")
# sanity check: itt group does not contain keyword bolus
# itt = itt %>% filter(randomization_allocation_assignment_list %in% c("Dex 0.1 mcg/kg/h", "Dex 0.3 mcg/kg/h", "Placebo"))
# pp = readRDS("data/rds/pp.rds")
mitt = readRDS("data/rds/mitt.rds")
adj = demo %>% select(sid, age, sex, race, ethnicity)
```

# Apply analytical samples
```{r}
# use mitt
outcome1 = outcome1 %>% filter(sid %in% mitt$sid)
group = group %>% filter(sid %in% mitt$sid)

# group2 to combine two Dex groups
group$group2 = group$group %>% as.character()
group$group2[group$group2 == "Dex 0.1 mcg/kg/h"] = "Dex"
group$group2[group$group2 == "Dex 0.3 mcg/kg/h"] = "Dex"
group$group2 = as.character(group$group2)

# left join
data1 = left_join(outcome1, group, by = "sid")
data1 = left_join(data1, adj, by = "sid")
data1 = data1 %>% filter(sid %in% mitt$sid)
```

```{r}
# adj_14day_DFD is the imputed DFD for in-hospital DFDs -> up to 14 days.
# clean up and set up variables

# make adj_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_DFDs) %>% sort()
data1$adj_DFDs = factor(data1$adj_DFDs, levels = levels, ordered = T)

# make unadj_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_DFDs) %>% sort()
data1$unadj_DFDs = factor(data1$unadj_DFDs, levels = levels, ordered = T)

# make adj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_ICU_DFDs) %>% sort()
data1$adj_ICU_DFDs = factor(data1$adj_ICU_DFDs, levels = levels, ordered = T)

# make unadj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_ICU_DFDs) %>% sort()
data1$unadj_ICU_DFDs = factor(data1$unadj_ICU_DFDs, levels = levels, ordered = T)

# set Placebo as the group reference
data1$group = factor(data1$group)
data1$group = relevel(data1$group, ref = "Placebo")

data1$group2 = as.factor(data1$group2)
data1$group2 = relevel(data1$group2, ref = "Placebo")

#janitor::tabyl(outcome1$adj_DFDs)
#janitor::tabyl(outcome1$unadj_DFDs)

covariate = demo %>% 
  select(sid, day_1_sofa_score, mean_iqcode_score, delirium_status,days_in_icu_pre_enrollment, days_in_hosp_pre_enrollment,obstructive_sleep_apnea_y_n,
         med_prestudy_benzos_yn,med_prestudy_phenobarbital_yn)
  
data1 = left_join(data1, covariate, by = "sid")
```

```{r}
# data1$delirium_status as 0/1
data1$delirium_status = case_when(
  data1$delirium_status == "N" ~ 0,
  data1$delirium_status == "Y" ~ 1
)

```

```{r}
data1 = data1 %>% mutate(t_icu = days_in_icu_pre_enrollment)
data1 = data1 %>% mutate(t_hosp = days_in_hosp_pre_enrollment)
```


```{r}
# this is settup group variables not important
group = group %>% mutate(group3g = group, group2g = group2, groupx = group)
# set group now
group = group %>% select(-group, -group2)
# in group now we only have groupx, which is different
group$groupx = group$group2g
#group$groupx = group$group3g
```
# choose 2 groups or 3 groups
```{r}
data1$group_2g = data1$group2
data1$group_3g = data1$group
data1 = data1 %>% select(-group2, -group)

# now new group2 = 2g or 3g
# data1 = data1 %>% mutate(group2 = group_2g)
data1 = data1 %>% mutate(group2 = group_3g)
```

Now we start analysis - distributions already checked up
- primary analysis start here
- group2 is group2g or group3g depending on the selection

# sen: add surg location
```{r}
locations = readRDS("data/rds/locations.rds")
data1_loc = left_join(data1, locations, by = "sid")
```

## imputed in-hosp DFDs
Note: adj in-hosp DFDs are calculated as imputed upto 14-day DFD.
```{r}
library(ordinal)
mod1 = clm(adj_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_loc, link = "logit")
# summary(mod1)
# brant.test(mod1)
# scale_test(mod1)
# tbl_regression(mod1,exponentiate = T,
#                       estimate_fun = function(x) style_ratio(x, digits = 3),
#                       pvalue_fun = function(x) style_pvalue(x, digits = 3))
mod1a = clm(adj_DFDs ~ group2 + age + mean_iqcode_score + delirium_status + t_icu + t_hosp + any_location_surgical, 
           data = data1_loc, link = "logit")
# summary(mod1a)
# brant.test(mod1a)
# scale_test(mod1a)
# tbl_regression(mod1a,exponentiate = T,
#                       estimate_fun = function(x) style_ratio(x, digits = 3),
#                       pvalue_fun = function(x) style_pvalue(x, digits = 3))



# LR test
anova(mod1, mod1a)
# conclusion: no model improvement by adding surgical location, so we will not include surgical location in the model.
```
## imputed in-ICU DFDs
```{r}
library(ordinal)
mod1 = clm(adj_ICU_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_loc, link = "logit")
# summary(mod1)
# brant.test(mod1)
# scale_test(mod1)
# tbl_regression(mod1,exponentiate = T,
#                       estimate_fun = function(x) style_ratio(x, digits = 3),
#                       pvalue_fun = function(x) style_pvalue(x, digits = 3))
mod1a = clm(adj_ICU_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp + any_location_surgical, 
           data = data1_loc, link = "logit")
# summary(mod1a)
# brant.test(mod1a)
# scale_test(mod1a)
# tbl_regression(mod1a,exponentiate = T,
#                       estimate_fun = function(x) style_ratio(x, digits = 3),
#                       pvalue_fun = function(x) style_pvalue(x, digits = 3))

# LR test
anova(mod1, mod1a)
# conclusion: no model improvement by adding surgical location, so we will not include surgical location in the model.
```

# sen: treat death within 14 days DFD as 0
- we are taking this conservative approach for SA
- we set any death within 14 days in hospital as 0
```{r}
death1 = readRDS("data/rds/surv1.rds")
data1_d0 = data1 %>% select(sid, adj_DFDs, adj_ICU_DFDs, group2, age, mean_iqcode_score, day_1_sofa_score, delirium_status, t_icu, t_hosp)
data1_d0 = left_join(data1_d0, death1 %>% select(sid,mortality_in_icu,mortality_in_hosp), by = "sid")
```


```{r}
CreateCatTable(data = data1_d0, vars = "mortality_in_icu",strata = "group2",test = F) %>% print(showAllLevels = T)
CreateCatTable(data = data1_d0, vars = "mortality_in_hosp",strata = "group2",test = F) %>% print(showAllLevels = T)
```

```{r}
# correct all DFDs to 0 if death within 14 days
# print, get mean(sd), and then change
data1_d0 %>% filter(mortality_in_hosp == "Y") %>% 
  select(sid, adj_DFDs) %>% 
  nrow() %>% 
  paste("mortality_in_hosp == Y, n =", ., "patients")

# how many is non-zero
data1_d0 %>% filter(mortality_in_hosp == "Y" & adj_DFDs>0) %>% 
  select(sid, adj_DFDs) %>% 
  nrow() %>% 
  paste("mortality_in_hosp == Y, non-zero n =", ., "patients, will be changed to 0")

# now re-code
data1_d0$adj_DFDs[data1_d0$mortality_in_hosp == "Y"] = 0
summary(data1_d0$adj_DFDs[data1_d0$mortality_in_hosp == "Y"])
```
```{r}
# now do the same for ICU DFDs
data1_d0 %>% filter(mortality_in_hosp == "Y") %>% 
  select(sid, adj_ICU_DFDs) %>% 
  nrow() %>% 
  paste("mortality_in_hosp == Y, n =", ., "patients")

data1_d0 %>% filter(mortality_in_hosp == "Y" & adj_ICU_DFDs>0) %>% 
  select(sid, adj_ICU_DFDs) %>% 
  nrow() %>% 
  paste("mortality_in_hosp == Y, non-zero n =", ., "patients, will be changed to 0")

# now re-code
data1_d0$adj_ICU_DFDs[data1_d0$mortality_in_hosp == "Y"] = 0
summary(data1_d0$adj_ICU_DFDs[data1_d0$mortality_in_hosp == "Y"])
```
## imputed in-hosp 14-day DFDs with death in hosp as 0
```{r}
library(gtsummary)
# rerun mv model
library(ordinal)
mod1 = clm(adj_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_d0, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

## imputed in-ICU DFDs with death in hosp as 0
```{r}
mod1 = clm(adj_ICU_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_d0, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```
# GAMLASS
```{r}
library(gamlss)
data1_gamlss = data1 %>% select(sid, adj_DFDs, adj_ICU_DFDs, group2, age, mean_iqcode_score, day_1_sofa_score, delirium_status, t_icu, t_hosp)

# change adj_DFDs as numeric
data1_gamlss$adj_DFDs_num = as.numeric(as.character(data1_gamlss$adj_DFDs))

mod1 <- gamlss(
  adj_DFDs_num ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,  # Formula for mu (location)
  sigma.formula = ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,  # Formula for sigma (scale)
  family = NO(),  # Assuming a normal distribution; adjust as appropriate
  data = data1_gamlss
)

summary(mod1)
```

```{r}
# change adj_ICU_DFDs as numeric
data1_gamlss$adj_ICU_DFDs_num = as.numeric(as.character(data1_gamlss$adj_ICU_DFDs))

mod1 <- gamlss(
  adj_ICU_DFDs_num ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,  # Formula for mu (location)
  sigma.formula = ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp,  # Formula for sigma (scale)
  family = NO(),  # Assuming a normal distribution; adjust as appropriate
  data = data1_gamlss
)

summary(mod1)
```
# re-ordering
- regroup in hospital DFDs by every 2 days, as some categories did not exist
- no need for ICU DFDs, as this issue did not exist.
```{r}

data1_relevel = data1 %>% select(sid, adj_DFDs, adj_ICU_DFDs, group2, age, mean_iqcode_score, day_1_sofa_score,delirium_status, t_icu, t_hosp)

# reduce DFD to every 2 days, so 7 levels
data1_relevel$adj_DFDs = as.numeric(as.character(data1$adj_DFDs))
# cut them by 2 days, so 0-2, 2-4, 4-6, 6-8, 8-10, 10-12, 12-14
data1_relevel$adj_DFDs = cut(data1_relevel$adj_DFDs, breaks = c(-0.001, 2, 4, 6, 8, 10, 12, 14), include.lowest = T)
# make it ordinal
data1_relevel$adj_DFDs = ordered(data1_relevel$adj_DFDs)
```

```{r}
mod1 = clm(adj_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_relevel, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```

```{r}
mod1 = clm(adj_ICU_DFDs ~ group2 + age + mean_iqcode_score + day_1_sofa_score + delirium_status + t_icu + t_hosp, 
           data = data1_relevel, link = "logit")
summary(mod1)
brant.test(mod1)
scale_test(mod1)
tbl_regression(mod1,exponentiate = T,
                      estimate_fun = function(x) style_ratio(x, digits = 3),
                      pvalue_fun = function(x) style_pvalue(x, digits = 3))
```
