---
title: "Sensitivity analysis: forest plot"
output: 
  html_notebook: 
    toc: true
    toc_depth: 4
    toc_float: true
    theme: simplex
    number_sections: true
    highlight: zenburn
    fig_width: 8
    fig_height: 6
    css: custom.css
---

```{r warning=FALSE , message=FALSE}
rm(list = ls())
library(tidyverse)
library(tableone)
library(openxlsx)
library(knitr)
library(magrittr)
library(janitor)
library(readxl)
library(ordinal)  # for clm()
library(clipr)    # for write_clip()
options(scipen=999)
library(readr)

# set width of the output
options(width = 120)
```

# Load data
```{r}
outcome1 = readRDS("data/rds/outcome1.rds")
group = readRDS("data/rds/group.rds")
demo = readRDS("data/rds/demo.rds")
itt = readRDS("data/rds/itt.rds")
# sanity check: itt group does not contain keyword bolus
# itt = itt %>% filter(randomization_allocation_assignment_list %in% c("Dex 0.1 mcg/kg/h", "Dex 0.3 mcg/kg/h", "Placebo"))
# pp = readRDS("data/rds/pp.rds")
mitt = readRDS("data/rds/mitt.rds")
adj = demo %>% select(sid, age, sex, race, ethnicity)
```

# Apply analytical samples
```{r}
# use mitt
outcome1 = outcome1 %>% filter(sid %in% mitt$sid)
group = group %>% filter(sid %in% mitt$sid)

# group2 to combine two Dex groups
group$group2 = group$group %>% as.character()
group$group2[group$group2 == "Dex 0.1 mcg/kg/h"] = "Dex"
group$group2[group$group2 == "Dex 0.3 mcg/kg/h"] = "Dex"
group$group2 = as.character(group$group2)

# left join
data1 = left_join(outcome1, group, by = "sid")
data1 = left_join(data1, adj, by = "sid")
data1 = data1 %>% filter(sid %in% mitt$sid)
```

```{r}
# adj_14day_DFD is the imputed DFD for in-hospital DFDs -> up to 14 days.

# make adj_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_DFDs) %>% sort()
data1$adj_DFDs = factor(data1$adj_DFDs, levels = levels, ordered = T)

# make unadj_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_DFDs) %>% sort()
data1$unadj_DFDs = factor(data1$unadj_DFDs, levels = levels, ordered = T)

# make adj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$adj_ICU_DFDs) %>% sort()
data1$adj_ICU_DFDs = factor(data1$adj_ICU_DFDs, levels = levels, ordered = T)

# make unadj_ICU_DFDs a factor but ordinal based on the numeric value
levels = unique(data1$unadj_ICU_DFDs) %>% sort()
data1$unadj_ICU_DFDs = factor(data1$unadj_ICU_DFDs, levels = levels, ordered = T)

# set Placebo as the group reference
data1$group = factor(data1$group)
data1$group = relevel(data1$group, ref = "Placebo")

data1$group2 = as.factor(data1$group2)
data1$group2 = relevel(data1$group2, ref = "Placebo")

#janitor::tabyl(outcome1$adj_DFDs)
#janitor::tabyl(outcome1$unadj_DFDs)

covariate = demo %>% 
  select(sid, day_1_sofa_score, mean_iqcode_score, delirium_status,days_in_icu_pre_enrollment, days_in_hosp_pre_enrollment,obstructive_sleep_apnea_y_n,
         med_prestudy_benzos_yn,med_prestudy_phenobarbital_yn)
  
data1 = left_join(data1, covariate, by = "sid")
```

```{r}
# data1$delirium_status as 0/1
data1$delirium_status = case_when(
  data1$delirium_status == "N" ~ 0,
  data1$delirium_status == "Y" ~ 1
)

```

```{r}
data1 = data1 %>% mutate(t_icu = days_in_icu_pre_enrollment)
data1 = data1 %>% mutate(t_hosp = days_in_hosp_pre_enrollment)
```

```{r}
# this is settup group variables not important
group = group %>% mutate(group3g = group, group2g = group2, groupx = group)
# set group now
group = group %>% select(-group, -group2)
# in group now we only have groupx, which is different
group$groupx = group$group2g
#group$groupx = group$group3g
```
# choose 2 groups or 3 groups
```{r}
data1$group_2g = data1$group2
data1$group_3g = data1$group
data1 = data1 %>% select(-group2, -group)

# now new group2 = 2g or 3g
# data1 = data1 %>% mutate(group2 = group_2g)
data1 = data1 %>% mutate(group2 = group_3g)
```


Now we start analysis - distributions already checked up
- primary analysis start here
- group2 is group2g or group3g depending on the selection

# Adjusted in-hosp DFDs
## age
```{r fig.height=6, fig.width=12}
library(performance)
test_data = data1 %>% select(adj_DFDs, group2, age) %>% mutate(age = if_else( age < 65, "Age < 65", "Age >= 65"))
# adjusted model
adjust = "age"
fit1 = paste0("adj_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_DFDs ~ group2*age, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | age, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = age,estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "Age")
emm4 = emm3 %>% mutate(estimate = exp(estimate), 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))
emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Age < 65", "Low", "High")
         )
  
emm_age = emm4; rm(emm4)
```

## mean_iqcode_score
We use 3.0 as cutoff. <= 3.0 normal, > 3.0 cognitive decline.
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_DFDs, group2, mean_iqcode_score) %>% 
  mutate(mean_iqcode_score = if_else( mean_iqcode_score <= 3, "Score <= 3", "Score > 3"))
# adjusted model
adjust = "mean_iqcode_score"
fit1 = paste0("adj_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_DFDs ~ group2*mean_iqcode_score, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | mean_iqcode_score, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = mean_iqcode_score, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "IQCODE Score (Mean)")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Score <= 3", "Low", "High")
         )

emm_iqcode = emm4; rm(emm4)
```

## day1_sofa_score
w use >=5 vs <5
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_DFDs, group2, day_1_sofa_score) %>% 
  mutate(day_1_sofa_score = if_else( day_1_sofa_score < 5, "Score < 5", "Score >= 5"))
# adjusted model
adjust = "day_1_sofa_score"
fit1 = paste0("adj_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_DFDs ~ group2*day_1_sofa_score, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | day_1_sofa_score, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = day_1_sofa_score, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "SOFA Score")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Score < 5", "Low", "High")
         )

emm_sofa_score = emm4; rm(emm4)
```

## delirium_status
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_DFDs, group2, delirium_status) %>% 
  mutate(delirium_status = if_else( delirium_status == 1, "Delirium = Y", "Delirium = N"))
# adjusted model
adjust = "delirium_status"
fit1 = paste0("adj_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_DFDs ~ group2*delirium_status, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | delirium_status, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = delirium_status, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "Delirium Status")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Delirium = N", "Low", "High")
         )

emm_delirium_status = emm4; rm(emm4)
```

```{r}
emm_all = rbind(emm_age,emm_iqcode,emm_sofa_score, emm_delirium_status)
write_clip(emm_all)
# emm_all_dex1 = emm_all %>% filter(contrast == "(Dex 0.1 mcg/kg/h) - Placebo")
# write_clip(emm_all_dex1)
# emm_all_dex2 = emm_all %>% filter(contrast == "(Dex 0.3 mcg/kg/h) - Placebo")
# write_clip(emm_all_dex2)
```



# Adjusted icu DFDs
## age
```{r fig.height=6, fig.width=12}
library(performance)
test_data = data1 %>% select(adj_ICU_DFDs, group2, age) %>% mutate(age = if_else( age < 65, "Age < 65", "Age >= 65"))
# adjusted model
adjust = "age"
fit1 = paste0("adj_ICU_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_ICU_DFDs ~ group2*age, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | age, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = age,estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "Age")
emm4 = emm3 %>% mutate(estimate = exp(estimate), 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))
emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Age < 65", "Low", "High")
         )
  
emm_age = emm4; rm(emm4)
```

## mean_iqcode_score
We use 3.0 as cutoff. <= 3.0 normal, > 3.0 cognitive decline.
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_ICU_DFDs, group2, mean_iqcode_score) %>% 
  mutate(mean_iqcode_score = if_else( mean_iqcode_score <= 3, "Score <= 3", "Score > 3"))
# adjusted model
adjust = "mean_iqcode_score"
fit1 = paste0("adj_ICU_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_ICU_DFDs ~ group2*mean_iqcode_score, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | mean_iqcode_score, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = mean_iqcode_score, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "IQCODE Score (Mean)")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Score <= 3", "Low", "High")
         )

emm_iqcode = emm4; rm(emm4)
```

## day1_sofa_score
w use >=5 vs <5
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_ICU_DFDs, group2, day_1_sofa_score) %>% 
  mutate(day_1_sofa_score = if_else( day_1_sofa_score < 5, "Score < 5", "Score >= 5"))
# adjusted model
adjust = "day_1_sofa_score"
fit1 = paste0("adj_ICU_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_ICU_DFDs ~ group2*day_1_sofa_score, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | day_1_sofa_score, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = day_1_sofa_score, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "SOFA Score")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Score < 5", "Low", "High")
         )

emm_sofa_score = emm4; rm(emm4)
```


## delirium_status
```{r}
# hist(data1$mean_iqcode_score)
library(performance)
test_data = data1 %>% 
  select(adj_ICU_DFDs, group2, delirium_status) %>% 
  mutate(delirium_status = if_else( delirium_status == 1, "Delirium = Y", "Delirium = N"))
# adjusted model
adjust = "delirium_status"
fit1 = paste0("adj_ICU_DFDs", " ~ group2*", adjust)
fit1
mod1 = clm(adj_ICU_DFDs ~ group2*delirium_status, data = test_data, link = "logit")

# get stratum-specific ORs
library(emmeans)
emm1 = emmeans(mod1, ~ group2 | delirium_status, type = "response")
emm2 = pairs(emm1, reverse = T, adjust = "none") %>% confint() %>% as.data.frame()
emm3 = emm2 %>% select(contrast, class = delirium_status, estimate,asymp.LCL, asymp.UCL) %>% mutate(variable = "Delirium Status")
emm4 = emm3 %>% mutate(estimate = exp(estimate) , 
                      asymp.LCL = exp(asymp.LCL), 
                      asymp.UCL = exp(asymp.UCL))

emm4 = emm4 %>% 
  mutate(error_positive = asymp.UCL - estimate, 
         error_negative = estimate - asymp.LCL,
         risk = ifelse(class == "Delirium = N", "Low", "High")
         )

emm_delirium_status = emm4; rm(emm4)
```

```{r}
emm_all = rbind(emm_age,emm_iqcode,emm_delirium_status,emm_sofa_score)
write_clip(emm_all)
# emm_all_dex1 = emm_all %>% filter(contrast == "(Dex 0.1 mcg/kg/h) - Placebo")
# write_clip(emm_all_dex1)
# emm_all_dex2 = emm_all %>% filter(contrast == "(Dex 0.3 mcg/kg/h) - Placebo")
# write_clip(emm_all_dex2)
```

